The development of infants' responses to mispronunciations - A Meta-Analysis

### 2018-11-24 Paper_Analyses.tex
small updates to manuscript, towards a final exploratory analysis

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{The development of infants' responses to mispronunciations - A
Meta-Analysis}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Katie Von Holzen\textsuperscript{1,2}~\& Christina
Bergmann\textsuperscript{3,4}}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \date{}
  \predate{}\postdate{}

\shorttitle{Mispronunciation Meta-Analysis}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Language Development Laboratory, University of Maryland, USA\\\textsuperscript{2} Laboratoire Psychologie de la Perception, Université Paris Descartes\\\textsuperscript{3} Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands\\\textsuperscript{4} LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University}
\keywords{keywords\newline\indent Word count: X}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

Acquiring a first language means that young learners are solving a host
of tasks in a short amount of time. As infants develop into toddlers
during their second and third years they learn new words in earnest
while simultaneously refining their knowledge about the sounds that make
up these words. Before children can correctly pronounce a word, they
already show evidence of sensitivity to slight variations in the
phonological form of that word. This mispronunciation sensitivity
reflects the specificity with which infants represent the phonological
information of familiar words and are sensitive to changes that might
signal a change in word meaning. As infants continue to develop into
expert language users, their language processing matures and becomes
more efficient. In a mature phono-lexical system, word recognition must
balance flexibility to slight variation (e.g., speaker identity,
accented speech) while distinguishing between phonetic details that
differentiate words in their native language (e.g.~cat-hat). In this
paper, we aggregate and analyze the almost 20 years of literature
investigating mispronunciation sensitivity in infants in an attempt to
uncover its characteristics and the trajectory of its development.

At the turn of the millenia, infant language acquisition researchers had
established that during their first years of life, infants are sensitive
to changes in the phonetic detail of newly segmented words (Jusczyk \&
Aslin, 1995) and learned minimal pairs (Stager \& Werker, 1997).
Furthermore, when presented with familiar image pairs, children fixate
on one image upon hearing its label (Fernald, Pinto, Swingley, Weinberg,
\& McRoberts, 1998). Swingley and Aslin (2000) were the first to tie
these lines of research together and investigate mispronunciation
sensitivity in infant familiar word recognition: Children aged 18 to 23
months learning American English were presented with pairs of images
(e.g.~baby, dog) and their eye movements to each image were coded
offline. On \enquote{correct} trials, children heard the correct label
for one of the images (e.g.~baby). On \enquote{mispronounced} trials,
children heard a mispronounced label of one of the images (e.g.~vaby).
Mean proportion of fixation to the target image (here: a baby) was
calculated for both correct and mispronounced trials by dividing the
target looking time by the sum of total looking time to both target and
a distractor (proportion of target looking or PTL). Mean fixations in
correct trials were significantly greater than in mispronounced trials,
although looks to the target were significantly greater than chance in
both types of trials. We refer to this pattern of a difference between
looks to correct and mispronounced words as \emph{mispronunciation
sensitivity} and of looks to the target image above chance as
\emph{recognition}. Swingley and Aslin (2000) concluded that already
before the second birthday, children represent words with sufficient
detail to be sensitive to mispronunciations.

The study of Swingley and Aslin (2000) as well as subsequent studies
examining mispronunciation sensitivity address two complementary
concepts in early phonological development: \emph{phonological
constancy} and \emph{phonological distinctiveness}. Phonological
constancy is the ability to accept phonological variation across
different instances of a word, as long as the variation does not
compromise the overall identity of the word. For example, different
speakers - particularly across genders and accents - produce the same
word with notable acoustic variation, although the word remains the
same. In contrast, phonological distinctiveness describes the ability to
differentiate between different words that happen to be phonologically
similar, such as bad/bed or cat/hat. To successfully recognize words,
infants must therefore simultaneously use both phonological constancy
and distinctiveness to determine where phonological variation is
appropriate and where it changes a word's meaning.

In the current study, we focus on infants' developing ability to
correctly apply the principles of phonological distinctiveness and
constancy by using a meta-analytic approach to investigate
mispronunciation sensitivity. Considering that infants are sensitive to
mispronunciations and that, in general, their processing matures with
development, we examine the shape of mispronunciation sensitivity over
the course of the second and third year. There are three distinct
possibilities how mispronunciation sensitivity might change as infants
become native speakers, which are all respectively predicted by
theoretical accounts and supported by single studies. By aggregating all
publicly available evidence using meta-analysis, we can examine
developmental trends making use of data from a much larger and diverse
sample of infants. Before we outline the meta-analytical approach and
its advantages in detail, we first discuss the proposals this study
seeks to disentangle and the data supporting each of the accounts.

Young infants may begin cautiously in their approach to word
recognition, rejecting any phonological variation in familiar words and
only later learning to accept appropriate variability. According to the
Perceptual Attunement account, this describes a shift away from specific
native phonetic patterns to a more mature understanding of the abstract
phonological structure of words (Best 1994, 1995). This shift is
predicted to coincide with the vocabulary spurt around 18 months, and is
therefore related to vocabulary growth. In this case, we would expect
the size of mispronunciation sensitivity to be larger at younger ages
and \emph{decrease} as the child matures and learn more words, although
children continue to detect mispronunciations. Indeed, young infants are
less likely than older infants to demonstrate recognition of familiar
words (Best, Tyler, Gooding, Orlando, \& Quann, 2009; Mulak, Best, \&
Tyler, 2013) or learn new words (Schmale, Hollich, \& Seidl, 2011) from
accented speakers.

@@

Research following the seminal study by Swingley and Aslin (2000) has
extended mispronunciation sensitivity to infants as young as 12 months
(Mani \& Plunkett, 2010), indicating that from early stages of the
developing lexicon onwards, infants can and do detect mispronunciations.
Regarding the change in mispronunciation sensitivity over development,
however, only a handful of studies have compared more than one age group
on the same mispronunciation task (see Table X), making the current
meta-analysis very informative. One study has found evidence for infants
to become \emph{less} sensitive to mispronunciations as children
develop. Mani and Plunkett (2011) presented 18- and 24-month-olds with
mispronunciations varying in the number of features changed (see below
for a discussion of the role of features). 18-month-olds were sensitive
to mispronunciations, regardless of the number of features changed.
24-month-olds, in contrast, fixated the target image equally for both
correct and 1-feature mispronounced trials, although they were sensitive
to larger mispronunciations. In other words, for 1-feature
mispronunciations at least, sensitivity decreased from 18 to 24 months,
providing support to the prediction that mispronunciation sensitivity
may decrease with development.

@@

Finally, some studies have found no difference in mispronunciation
sensitivity at different ages. Swingley and Aslin (2000) tested infants
over a wide age range of 5 months (18 to 23 months). They found that age
correlated with target fixations for both correct and mispronounced
labels, whereas the difference between the two (mispronunciation effect)
did not. This suggests that as children develop, they are more likely to
look at the target in the presence of a mispronounced label and that age
is not related to mispronunciation sensitivity. A similar response
pattern has been found for British English learning infants aged between
18 and 24 months (Bailey \& Plunkett, 2002) as well as younger
French-learning infants at 12 and 17 months (Zesiger, Lozeron, Levy, \&
Frauenfelder, 2012). These studies award support to the prediction that
mispronunciation sensitivity does not change with development.

@@

Yet, the majority of studies examining a potential association between
mispronunciation sensitivity and vocabulary size have concluded that
there is no relationship (Swingley \& Aslin 2000; 2002; Bailey \&
Plunkett, 2002; Zesiger, Lozeron, Levy, \& Frauenfelder, 2012; Swingley,
2009; Ballem \& Plunkett, 2005; Mani \& Plunkett, 2007; Mani, Coleman,
\& Plunkett, 2008). One notable exception comes from Mani and Plunkett
(2010: keps and tups). Here, 12-month-old infants were divided into a
low vocabulary and high vocabulary group based group median vocabulary
size. High vocabulary infants showed greater sensitivity to vowel
mispronunciations than low vocabulary infants, although this was not the
case for consonant mispronunciations. Taken together, although receiving
considerable support from theories of phono-lexical processing in
language acquisition, there is very little evidence for a role of
vocabulary size in mispronunciation sensitivity. In our current
meta-analysis, we include the relationship between mispronunciation
sensitivity and vocabulary size to further disentangle the disconnect
between theory and experimental results.

Taken together, the studies we have reviewed begin to paint a picture of
the development of mispronunciation sensitivity. Each study contributes
one separate brushstroke and it is only by examining all of them
together that we can achieve a better understanding. Meta-analyses can
not only help us summarize the current state of research, but can also
help us evaluate theories to drive future research and make hands-on
recommendations for experiment planning.

@@

The present meta-analysis was conducted with maximal transparency and
reproducibility in mind. To this end, we provide all data and analysis
scripts on the supplementary website (\url{https://osf.io/rvbjs/}) and
open our meta-analysis up for updates (Tsuji, Bergmann, \& Cristia,
2014). The most recent version is available via the website and the
interactive platform MetaLab (metalab.stanford.edu; Bergmann et al.,
2018). Since the present paper was written with embedded analysis
scripts in R {[}@R{]}, it is always possible to re-analyze an updated
dataset. In addition, we follow the Preferred Reporting Items for
Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the
corresponding information available as supplementary materials (Moher,
Liberati, Tetzlaff, Altman \& PRISMAGroup, 2009). Figure X plots our
PRISMA flowchart.

@@

\begin{tabular}{l|l|l|l}
\hline
Paper & Publication format & Age & Vocabulary\\
\hline
Altvater-Mackensen (2010) & dissertation & 22, 25 & None\\
\hline
Altvater-Mackensen et al. (2014) & paper & 18, 25 & None\\
\hline
Bailey \& Plunkett (2002) & paper & 18, 24 & Comprehension\\
\hline
Bergelson \& Swingley (2017) & paper & 7, 9, 12, 6 & None\\
\hline
Bernier \& White 2017 & proceedings & 21 & None\\
\hline
Delle Luche et al. (2015) & paper & 20, 19 & None\\
\hline
Durrant et al. (2014) & paper & 19, 20 & None\\
\hline
Hoehle et al. 2006 & paper & 18 & None\\
\hline
Hojen et al. & gray paper & 20 & Comprehension/Production\\
\hline
Mani \& Plunkett 2007 & paper & 15, 18, 24, 14, 21 & Comprehension/Production\\
\hline
Mani \& Plunkett 2010 & paper & 12 & Comprehension\\
\hline
Mani \& Plunkett 2011 & paper & 23, 17 & None\\
\hline
Mani, Coleman, \& Plunkett (2008) & paper & 18 & Comprehension/Production\\
\hline
Ramon-Casas \& Bosch 2010 & paper & 24, 25 & None\\
\hline
Ramon-Casas et al. 2009 & paper & 21, 20 & Production\\
\hline
Ren \& Morgan, in press & gray paper & 19 & None\\
\hline
Skoruppa et al. 2013 & paper & 24 & None\\
\hline
Swingley (2009) & paper & 17 & Comprehension/Production\\
\hline
Swingley (2016) & paper & 27, 28 & Production\\
\hline
Swingley \& Aslin (2000) & paper & 20 & Comprehension\\
\hline
Swingley \& Aslin (2002) & paper & 15 & Comprehension/Production\\
\hline
Swingley 2003 & paper & 19 & Comprehension/Production\\
\hline
Tamasi (2016) & dissertation & 30 & None\\
\hline
Tao \& Qinmei 2013 & paper & 12 & None\\
\hline
Tao et al. 2012 & paper & 16 & Comprehension\\
\hline
van der Feest \& Fikkert, 2015 & paper & 24, 20 & None\\
\hline
van der Feest \& Johnson, 2016 & paper & 24 & None\\
\hline
Wewalaarachchi et al. 2017 & paper & 24 & None\\
\hline
White \& Aslin (2011) & paper & 18 & None\\
\hline
White \& Morgan (2008) & paper & 18, 19 & None\\
\hline
Zesiger \& Johr 2011 & paper & 14 & None\\
\hline
Zesiger et al. (2012) & paper & 12, 19 & Comprehension/Production\\
\hline
\end{tabular}

{[}KATIE{]} THIS TABLE IS DEFINITELY NOT FINISHED! {[}CHRISTINA
suggestions: N features should be a range and exclude 0; we could
abbreviate Comperehension/Production to Comp./Prod.,
etcetc{]}{[}KATIE{]} I've reduced the table to be about age and
vocabulary, in order to have it more focused for the aim of this paper.

We first generated a list of potentially relevant items to be included
in our meta-analysis by creating an expert list. This process yielded
110 items. We then used the google scholar search engine to search for
papers citing the original Swingley \& Aslin (2000) publication. This
search was conducted on 22 September, 2017 and yielded 288 results. We
screened the 398 items, removing 99 duplicate items. We screened
remaining 299 items for their title and abstract to determine whether it
met the following inclusion criteria: (1) original data was reported;
(2) the experiment examined familiar word recognition; (3) infants
studied were under 36-months-of-age; (4) the dependent variable was
derived from proportion of looks to a target image versus a distractor
in a eye movement experiment; 5) the stimuli were auditory speech. The
final sample (n = \emph{32}) consisted of 27 journal articles, 1
proceedings paper, 2 thesis, and 2 unpublished reports. We will refer to
these items collectively as papers. Table 1 (Summary Table) provides an
overview of all papers included in the present meta-analysis.

@@

The 32 papers we identified as relevant were then coded with as much
detail as possible (Tsuji, Bergmann, \& Cristia, 2014; Bergmann et al.,
2018). For each experiment (note that a paper typically has multiple
experiments), we entered variables describing the publication,
population, experiment design and stimuli, and results. For the present
analyses, we focus on the following characteristics:

@@

We separated out conditions according to whether or not the target word
was mispronounced to be able to investigate infants' looking to the
target picture separated by whether or not words were mispronounced as
well as their mispronunciation sensitivity, which is the difference
between looks to the target in correct and mispronounced trials. When
the same infants were further exposed to multiple mispronunciation
conditions and the results were reported separately in the paper, we
also entered each condition as a separate row (e.g., consonant versus
vowel mispronunciations; Mani \& Plunkett, 2007). The fact that the same
infants contributed data to multiple rows (minimally those containing
information on correct and mispronounced trials) leads to shared
variance across effect sizes, which we account for in our analyses (see
next section). We will call each row a record; in total there were 251
records in our data.

@@

Mispronunciation sensitivity studies typically examine infants'
proportion of target looks (PTL) in comparison to a baseline
measurement. PTL is calculated by dividing the percentage of looks to
the target by the total percentage of looks to both the target and
distractor images. Across papers the baseline comparison varied; we used
the baseline reported by the authors of each paper. Most papers
(\emph{n} = 13) subtracted the PTL score for a pre-naming phase from the
PTL score for a post-naming phase. When interpreting this difference
score, a positive value indicates that infants increased their looks to
the target after hearing the naming label (correct or mispronounced).
Other papers either compared post- and pre-naming PTL with one another
(\emph{n} = 10) or compared post-naming PTL with a chance level of 50\%,
(\emph{n} = 9). For all these comparisons, a positive difference score
or a post-naming phase PTL score that is greater than the pre-naming
phase PTL or chance indicate target looks that indicate object
recognition after hearing the naming label. Consequently, positive
effect sizes reflect more looks to the target picture after naming, and
larger positive effect sizes indicate comparatively more relative
increase in looks to the target.

@@

We calculated Hedges' \emph{g} using the raw means and standard
deviations reported in the paper (\emph{n} = 2) or using reported
t-values (\emph{n} = 2). Raw means and standard deviations were
extracted from figures for 3 papers. In a within-participation design,
when two means are compared (i.e.~looking during pre- and post-naming)
it is necessary to obtain correlations between the two measurements at
the participant level to calculate effect sizes and effect size variance
based on t-values. Upon request we were provided with correlation values
for one paper (Altvater-Mackensen, 2010); we were able to compute
correlations using means, standard deviations, and t-values for \emph{n}
= 4 (following Csibra, et al. 2016, Appendix B; see also Rabagliati,
Ferguson, \& Lew-Williams, 2018). Correlations were imputed for the
remaining papers (see Black \& Bergmann, 2017, for the same procedure).
We could compute a total of 104 effect sizes for correct pronunciations
and 147 for mispronunciations.

@@

We should also point out that funnel plot asymmetry can be caused by
multiple factors beside publication bias. The funnel plot asymmetry may
also reflect heterogeneity in the data, perhaps due to some studies
investigating more subtle effects than other studies. {[}CHRISTINA: I
have to add some bits here.{]}

>>>>

  \title{The development of infants' responses to mispronunciations - A
Meta-Analysis}
    \author{Katie Von Holzen\textsuperscript{1,2}~\& Christina
Bergmann\textsuperscript{3,4}}
    \date{}

\shorttitle{Mispronunciation Meta-Analysis}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Department of Hearing and Speech Sciences, University of Maryland, USA\\\textsuperscript{2} Laboratoire Psychologie de la Perception, Université Paris Descartes\\\textsuperscript{3} Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands\\\textsuperscript{4} LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University}
\keywords{keywords\newline\indent Word count: X}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

Acquiring a first language means that young learners are solving a host
of tasks in a short amount of time. As infants develop into toddlers
during their second and third years they learn new words in earnest
while simultaneously refining their knowledge about the sounds that make
up these words {[}Primir, Kuhl, Best{]}. In a mature phono-lexical
system, word recognition must balance flexibility to slight variation
(e.g., speaker identity, accented speech) while distinguishing between
phonetic details that differentiate words in their native language
(e.g.~cat-hat). To build robust language knowledge, it seems ueful to
acquire this ability early during development. Indeed, before children
can correctly pronounce a word, they already are aware that slight
phonological deviations might signal a change in word meaning {[}Clark
\& Clark, 1977{]}. This mispronunciation sensitivity reflects the
specificity with which infants represent the phonological information of
familiar words. As infants continue to develop into expert language
users, their language processing matures and becomes more efficient,
including their knowledge of what consistutes a permissible versus
word-changing phonological deviation. In this paper, we aggregate and
analyze the almost 20 years of literature investigating mispronunciation
sensitivity in infants in an attempt to uncover its characteristics and
the trajectory of its development.

At the turn of the millenia, infant language acquisition researchers had
established that during their first years of life, infants are sensitive
to changes in the phonetic detail of newly segmented words (Jusczyk \&
Aslin, 1995) and learned minimal pairs (Stager \& Werker, 1997).
Furthermore, when presented with familiar image pairs, children fixate
on one image upon hearing its label (Fernald, Pinto, Swingley, Weinberg,
\& McRoberts, 1998; Tincoff \& Jusczyk, 1999). Swingley and Aslin (2000)
were the first to tie these lines of research together and investigate
mispronunciation sensitivity in infant familiar word recognition:
Children aged 18 to 23 months learning American English saw pairs of
images (e.g.~a baby and a dog) and their eye movements to each image
were recorded and subsequently coded offline. On \enquote{correct}
trials, children heard the correct label for one of the images (e.g.
\enquote{baby}). On \enquote{mispronounced} trials, children heard a
mispronounced label of one of the images (e.g. \enquote{vaby}). The mean
proportion of fixations to the target image (here: a baby) was
calculated separately for both correct and mispronounced trials by
dividing the target looking time by the sum of total looking time to
both target and a distractor (proportion of target looking or PTL). Mean
fixations in correct trials were significantly greater than in
mispronounced trials, and in both conditions looks to the target were
significantly greater than chance. We refer to this pattern of a
difference between looks to correct and mispronounced words as
\emph{mispronunciation sensitivity} and of looks to the target image
above chance in each condition as \emph{object identification}. Swingley
and Aslin (2000) concluded that already before the second birthday,
children represent words with sufficient detail to be sensitive to
mispronunciations.

{[}Christina: changed concepts to mechanisms in the next paragraph,
because I want to refer to what they represent, but I am not sure it's
the right term{]}{[}Katie: Karen (Mulak) talks about these terms as
concepts. Mechanisms to me means some sort of internalization, that they
would have had this ability all along and just need to apply it. It
could be that we fundamentally disagree on this, but to me these are
things that infants discover. Later on we use principles. What about
\enquote{principles that infants must discover}\ldots{} \enquote{in
order to form adult-like word representations}? I took away
\enquote{which are both present in the mature language processing
system}.{]}

The study of Swingley and Aslin (2000) as well as subsequent studies
examining mispronunciation sensitivity address two complementary
principles that infants must discover in early phonological development
in order to form adult-like word representations: \emph{phonological
constancy} and \emph{phonological distinctiveness}. Phonological
constancy is the ability to resolve phonological variation across
different instances of a word, as long as the variation does not
compromise the overall identity of the word. For example, different
speakers - particularly across genders and accents - produce the same
word with notable acoustic variation, although the word remains the
same. In contrast, phonological distinctiveness describes the ability to
differentiate between different words that happen to be phonologically
similar, such as bad/bed or cat/hat. To successfully recognize words,
speakers of a given language must therefore simultaneously use both
phonological constancy and distinctiveness to determine where
phonological variation is appropriate and where it changes a word's
meaning. Both abilities have to be acquired, because language systems
differ in which sounds signal a meaning change.

{[}Katie: since we actually don't have theoretical framework support for
the no-change theory, I've changed around the sentence below to
explicitly say that only 2 of the 3 are predicted by theoretical
accounts.{]}

In the current study, we focus on infants' developing ability to
correctly apply the principles of phonological distinctiveness and
constancy by using a meta-analytic approach to investigate
mispronunciation sensitivity. Considering that infants are sensitive to
mispronunciations and that, in general, their processing matures with
development, we examine the shape of mispronunciation sensitivity over
the course of the second and third year. There are three distinct
possibilities how mispronunciation sensitivity might change as infants
become native speakers, which are all respectively supported by single
studies and two predicted by theoretical accounts. By aggregating all
publicly available evidence using meta-analysis, we can examine
developmental trends making use of data from a much larger and diverse
sample of infants than is possible in most single studies (see Frank et
al., 2018; for a notable exception). Before we outline the
meta-analytical approach and its advantages in detail, we first discuss
the proposals this study seeks to disentangle and the data supporting
each of the accounts.

Young infants may begin cautiously in their approach to word
recognition, rejecting any phonological variation in familiar words and
only later learning to accept appropriate variability. According to the
Perceptual Attunement account, this describes a shift away from specific
native phonetic patterns to a more mature understanding of the abstract
phonological structure of words (Best 1994, 1995). This shift is
predicted to coincide with the vocabulary spurt around 18 months, and is
therefore related to vocabulary growth. In this case, we would expect
the size of mispronunciation sensitivity to be larger at younger ages
and \emph{decrease} as the child matures and learn more words, although
children continue to detect mispronunciations. Indeed, young infants are
more perturbed by accented speakers than older infants in their
recognition of familiar words (Best, Tyler, Gooding, Orlando, \& Quann,
2009; Mulak, Best, \& Tyler, 2013) or learning of new words (Schmale,
Hollich, \& Seidl, 2011).

@@

Research following the seminal study by Swingley and Aslin (2000) has
extended mispronunciation sensitivity to infants as young as 9 months
(Bergelson \& Swingley, 2017), indicating that from early stages of the
developing lexicon onwards, infants can and do detect mispronunciations.
Regarding the change in mispronunciation sensitivity over development,
however, only a handful of studies have compared more than one age group
on the same mispronunciation task (see Table X), making the current
meta-analysis very informative. One study has found evidence for infants
to become \emph{less} sensitive to mispronunciations as children
develop. Mani and Plunkett (2011) presented 18- and 24-month-olds with
mispronunciations varying in the number of features changed (see below
for a discussion of the role of features). 18-month-olds were sensitive
to mispronunciations, regardless of the number of features changed.
24-month-olds, in contrast, fixated the target image equally for both
correct and 1-feature mispronounced trials, although they were sensitive
to larger mispronunciations. In other words, for 1-feature
mispronunciations at least, sensitivity decreased from 18 to 24 months,
providing support to the prediction that mispronunciation sensitivity
may decrease with development.

@@

Finally, some studies have found no difference in mispronunciation
sensitivity at different ages. Swingley and Aslin (2000) tested infants
over a wide age range of 5 months (18 to 23 months). They found that age
correlated with target fixations for both correct and mispronounced
labels, whereas the difference between the two (mispronunciation
sensitivity) did not. This suggests that as children develop, they are
more likely to look at the target in the presence of a mispronounced
label and that age is not related to mispronunciation sensitivity. A
similar response pattern has been found for British English learning
infants aged between 18 and 24 months (Bailey \& Plunkett, 2002) as well
as younger French-learning infants at 12 and 17 months (Zesiger,
Lozeron, Levy, \& Frauenfelder, 2012). These studies award support to
the prediction that mispronunciation sensitivity does not change with
development.

@@

Yet, the majority of studies examining a potential association between
mispronunciation sensitivity and vocabulary size have concluded that
there is no relationship (Swingley \& Aslin 2000; 2002; Bailey \&
Plunkett, 2002; Zesiger, Lozeron, Levy, \& Frauenfelder, 2012; Swingley,
2009; Ballem \& Plunkett, 2005; Mani \& Plunkett, 2007; Mani, Coleman,
\& Plunkett, 2008). One notable exception comes from Mani and Plunkett
(2010: keps and tups). Here, 12-month-old infants were divided into a
low and high vocabulary group based on median vocabulary size. High
vocabulary infants showed greater sensitivity to vowel mispronunciations
than low vocabulary infants, although this was not the case for
consonant mispronunciations. Taken together, although receiving
considerable support from theories of phono-lexical processing in
language acquisition, there is very little evidence for a role of
vocabulary size in mispronunciation sensitivity. In our current
meta-analysis, we include the relationship between mispronunciation
sensitivity and vocabulary size to further disentangle the disconnect
between theory and experimental results.

In sum, the studies we have reviewed begin to paint a picture of the
development of mispronunciation sensitivity. Each study contributes one
separate brushstroke and it is only by examining all of them together
that we can achieve a better understanding of early language
development. Meta-analyses can provide thus further insights by
estimating the population effect, both of infants' responses to correct
and mispronounced labels, and their mispronunciations sensitivity.
Because we aggregate data over various age groups, this meta-analysis
can also investigate the role of maturation by assessing the impact of
age and vocabulary size. As a consequence, our results will be important
in evaluating theories and drive future research. We also make hands-on
recommendations for experiment planning, for example by providing an
effect size estimate for a priori power analyses (Bergmann et al.,
2018).

@@

The present meta-analysis was conducted with maximal transparency and
reproducibility in mind. To this end, we provide all data and analysis
scripts on the supplementary website (\url{https://osf.io/rvbjs/}) and
open our meta-analysis up for updates (Tsuji, Bergmann, \& Cristia,
2014). The most recent version is available via the website and the
interactive platform MetaLab (metalab.stanford.edu; Bergmann et al.,
2018). Since the present paper was written with embedded analysis
scripts in R {[}@R, @RMarkdown, @papaja{]}, it is always possible to
re-analyze an updated dataset. In addition, we follow the Preferred
Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA)
guidelines and make the corresponding information available as
supplementary materials (Moher, Liberati, Tetzlaff, Altman \&
PRISMAGroup, 2009). Figure X plots our PRISMA flowchart illustrating the
paper selection procedure.

@@

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:SummaryTable}Summary of all studies.}
\begin{tabular}{llll}
\toprule
Paper & Publication format & Age & Vocabulary\\
\midrule
Altvater-Mackensen (2010) & dissertation & 22, 25 & None\\
Altvater-Mackensen et al. (2014) & paper & 18, 25 & None\\
Bailey \& Plunkett (2002) & paper & 18, 24 & Comp\\
Bergelson \& Swingley (2017) & paper & 7, 9, 12, 6 & None\\
Bernier \& White 2017 & proceedings & 21 & None\\
Delle Luche et al. (2015) & paper & 20, 19 & None\\
Durrant et al. (2014) & paper & 19, 20 & None\\
Hoehle et al. 2006 & paper & 18 & None\\
Hojen et al. & gray paper & 20 & Comp/Prod\\
Mani \& Plunkett 2007 & paper & 15, 18, 24, 14, 21 & Comp/Prod\\
Mani \& Plunkett 2010 & paper & 12 & Comp\\
Mani \& Plunkett 2011 & paper & 23, 17 & None\\
Mani, Coleman, \& Plunkett (2008) & paper & 18 & Comp/Prod\\
Ramon-Casas \& Bosch 2010 & paper & 24, 25 & None\\
Ramon-Casas et al. 2009 & paper & 21, 20 & Prod\\
Ren \& Morgan, in press & gray paper & 19 & None\\
Skoruppa et al. 2013 & paper & 24 & None\\
Swingley (2009) & paper & 17 & Comp/Prod\\
Swingley (2016) & paper & 27, 28 & Prod\\
Swingley \& Aslin (2000) & paper & 20 & Comp\\
Swingley \& Aslin (2002) & paper & 15 & Comp/Prod\\
Swingley 2003 & paper & 19 & Comp/Prod\\
Tamasi (2016) & dissertation & 30 & None\\
Tao \& Qinmei 2013 & paper & 12 & None\\
Tao et al. 2012 & paper & 16 & Comp\\
van der Feest \& Fikkert, 2015 & paper & 24, 20 & None\\
van der Feest \& Johnson, 2016 & paper & 24 & None\\
Wewalaarachchi et al. 2017 & paper & 24 & None\\
White \& Aslin (2011) & paper & 18 & None\\
White \& Morgan (2008) & paper & 18, 19 & None\\
Zesiger \& Johr 2011 & paper & 14 & None\\
Zesiger et al. (2012) & paper & 12, 19 & Comp/Prod\\
\bottomrule
\end{tabular}
\end{threeparttable}
\end{center}
\end{table}

{[}Christina{]} I've shortened the labels and wanted to try out
apa\_table {[}Katie{]} I like the idea, but does it work for you? It
doesn't work for me\ldots{} {[}Katie{]} We have it currently set at less
than 31 months, not 36, so I've changed below.

We first generated a list of potentially relevant items to be included
in our meta-analysis by creating an expert list. This process yielded
110 items. We then used the google scholar search engine to search for
papers citing the original Swingley \& Aslin (2000) publication. This
search was conducted on 22 September, 2017 and yielded 288 results. We
screened the resulting 398 items, removing 99 duplicate items. We
screened remaining 299 items for their title and abstract to determine
whether it met the following inclusion criteria: (1) original data was
reported; (2) the experiment examined familiar word recognition and
mispronunciations; (3) infants studied were under 31-months-of-age; (4)
the dependent variable was derived from proportion of looks to a target
image versus a distractor in a eye movement experiment; (5) the stimuli
were auditory speech. The final sample (n = \emph{32}) consisted of 27
journal articles, 1 proceedings paper, 2 thesis, and 2 unpublished
reports. We will refer to these items collectively as papers. Table 1
(Summary Table) provides an overview of all papers included in the
present meta-analysis.

@@

The 32 papers we identified as relevant were then coded with as much
consistently reported detail as possible (Tsuji, Bergmann, \& Cristia,
2014; Bergmann et al., 2018). For each experiment (note that a paper
typically has multiple experiments), we entered variables describing the
publication, population, experiment design and stimuli, and results. For
the analyses presented in this section, we focus on the following
characteristics:

@@

We separated conditions according to whether or not the target word was
mispronounced to be able to investigate infants' looking to the target
picture as well as their mispronunciation sensitivity, which is the
difference between looks to the target in correct and mispronounced
trials. When the same infants were further exposed to multiple
mispronunciation conditions and the results were reported separately in
the paper, we also entered each condition as a separate row (e.g.,
consonant versus vowel mispronunciations; Mani \& Plunkett, 2007). The
fact that the same infants contributed data to multiple rows (minimally
those containing information on correct and mispronounced trials) leads
to shared variance across effect sizes, which we account for in our
analyses (see next section). We will call each row a record; in total
there were 251 records in our data.

@@

{[}Christina{]} I think it would be useful to say how many records, not
papers, report each measure. e.g. \enquote{(n = xxx records from yyy
papers)}. Would that be ok? {[}Katie{]} Totally! I think that gives a
good bit of information. Good suggestion!

Mispronunciation sensitivity studies typically examine infants'
proportion of target looks (PTL) in comparison to some baseline
measurement. PTL is calculated by dividing the percentage of looks to
the target by the total percentage of looks to both the target and
distractor images. Across papers the baseline comparison varied; we used
the baseline reported by the authors of each paper. Most papers
(\emph{n} = 52 records from 13 papers) subtracted the PTL score for a
pre-naming phase from the PTL score for a post-naming phase and report a
difference score.

{[}Christina{]} Katie, do you know whether the difference is computed
based on items, participants, trials\ldots{}? Is there consistency?
{[}Katie{]} From working with Nivi, we did it participants x condition
or participants x trial (but mostly the former). But, this is not
something we reported in papers. I don't think I read it at all when
putting together the dataset for this either.

Other papers either compared post- and pre-naming PTL with one another
(\emph{n} = 29 records from 10 papers), thus reporting two variables, or
compared post-naming PTL with a chance level of 50\%, (\emph{n} = 23
records from 9 papers). For all these comparisons, positive values
(either as reported or after subtraction of chance level or a pre-naming
PTL) indicate target looks towards the target object after hearing the
label, i.e.~a recognition effect. Standardized effect sizes based on
mean differences, as calculated here, preserve the sign. Consequently,
positive effect sizes reflect more looks to the target picture after
naming, and larger positive effect sizes indicate comparatively more
looks to the target.

@@

{[}Christina{]} These numbers seem wrong! Again, how about (xx effect
sizes from yy papers)? {[}Katie{]} Well, they are kind of wrong :) Two
papers report both for different experimental conditions. I've given the
explanation now, not sure if that is good enough, but I'm really not
sure how to say it a different way. {[}Katie{]} Do you want number of
records and papers for the imputed correlations as well? You've put a
-1, assuming there was something wrong with one of the papers or
something like that? How does that shake out for number of records?

We calculated Hedges' \emph{g} using the raw means and standard
deviations reported in the paper (\emph{n} = 177 records from 25 papers)
or using reported t-values (\emph{n} = 74 records from 9 papers). Two
papers reported raw means and standard deviations for some experimental
conditions and just t-values for the remaining experimental conditions
(Swingley, 2016; Altvater-Mackensen et al., 2014). Raw means and
standard deviations were extracted from figures for 3 papers. In a
within-participation design, when two means are compared (i.e.~looking
during pre- and post-naming) it is necessary to obtain correlations
between the two measurements at the participant level to calculate
effect sizes and effect size variance based on t-values. Upon request we
were provided with correlation values for one paper (Altvater-Mackensen,
2010); we were able to compute correlations using means, standard
deviations, and t-values for \emph{n} = 4 (following Csibra, et al.
2016, Appendix B; see also Rabagliati, Ferguson, \& Lew-Williams, 2018).
Correlations were imputed for the remaining papers (see Black \&
Bergmann, 2017, for the same procedure). We could compute a total of 104
effect sizes for correct pronunciations and 147 for mispronunciations.

@@

We should also point out that funnel plot asymmetry can be caused by
multiple factors beside publication bias. The funnel plot asymmetry may
also reflect heterogeneity in the data. There are various possible
sources of heterogeneity, which our subsequent moderator analyses will
begin to address. Nonetheless, we will remain cautious in our
interpretation of our findings and hope that an open dataset that can be
expanded by the community will attract previously unpublished null
results so we can better understand infants' developing mispronunciation
sensitivity.
